Figures and Tables

### 2021-02-05 paper/figures_tables.Rmd
add table of conditional probabilities for evd

```{r}
load("paper/fevd.RData")
```

@@

>>>>

```{r}
load("paper/resampling_evd_densplots.RData")
```

@@

```{r eval=FALSE, fig.width=6, fig.height=9}

plot_grid(null_boot_plot,
          indiv_boot_plot,
          fam_boot_plot,
          nrow = 3)
```

### Probabilities

```{r}
dist_range <- c(250, 500, 1000, 1250, 1500, 1750, 2000)
null_probs <- pextRemes(null_fit, dist_range, lower.tail = FALSE)
indiv_probs <- pextRemes(indiv_fit, dist_range, lower.tail = FALSE)
fam_probs <- pextRemes(fam_fit, dist_range, lower.tail = FALSE)

evd_probs <- as.data.frame(rbind(null_probs, indiv_probs, fam_probs))
names(evd_probs) <- dist_range
row.names(evd_probs) <- c("Null", "Individual", "Family")

knitr::kable(evd_probs)
```
